Resubmission of JMLR-14-133: Point-to-Point Reply

### 2014-09-08 pkg/partykit/inst/mloss/review2/p2p.tex
rephrase
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@608 255f4249-2263-4417-b1ea-8498779e27a7
resubmission
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@610 255f4249-2263-4417-b1ea-8498779e27a7

\title{Revision of JMLR-14-133: Point-to-Point Reply}
\author{Torsten Hothorn and Achim Zeileis}

@@

We hope that this is suitable for consideration in the MLOSS track of JMLR now.

>>>>

\title{Resubmission of JMLR-14-133: Point-to-Point Reply}
\author{Torsten Hothorn and Achim Zeileis}

@@

We hope that the \emph{partykit} package and the four-page description are
suitable for consideration in the MLOSS track of JMLR now.
